---
title: "SDS 315 Homework 4"
output: html_document
date: "2024-02-20"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE, message=FALSE}
library(ggplot2)
library(mosaic)
library(tidyverse)
gas <- read.csv('gasprices.csv')
mercedes <- read.csv('sclass.csv')
nbc_shows <- read.csv('nbc_pilotsurvey.csv')
ebay <- read.csv('ebay.csv')
```
# Problem 1 

## Part A
```{r echo=FALSE, message=FALSE}
gas_competitor = do(10000)*diffmean(Price ~ Competitors,
data=resample(gas))
ggplot(gas_competitor) + 
  geom_histogram(aes(x= diffmean), col = 'black', fill = 'lightpink') + labs(title = 'Distribution of the Difference Mean of Competitors and Gas Prices', x='Diffmean of Competitor and Price') + theme_minimal()
confint(gas_competitor, level = 0.95)
```
### Description:
The claim for this section is that Austin gas stations charge more if they lack direct competition in sight. To be able to prove this theory, there was a bootstrap sample done with the gas station price and the competitors in Austin. After doing the boot strap sample 10,000 times, the evidence shows that the difference in price between gas stations and competitors is somewhere between -0.05566 and 0.00733, with 95% confidence. The histogram is the visual summary of this theory and shows the distribution of the difference mean between competitors and price (x axis). The graph is approximately symmetrical. The mean is approximately `r round(mean(gas_competitor$diffmean),2)`. It is concluded that the theory is not supported because the 95% confidence interval does contain 0, so the mean difference is thus “statistically insignificant” at the 5% level.

## Part B
```{r echo=FALSE, message=FALSE}
lm_income = do(10000)*lm(Price ~ Income, data=mosaic::resample(gas))
confint(lm_income, level = 0.95) %>% filter(name == 'Income')
ggplot(gas) + 
  geom_jitter(aes(x = Income, y = Price), col = 'black', fill = 'red', alpha = 0.1) + 
  geom_smooth(aes(x = Income, y = Price), method = 'lm') + labs(title = 'Relationship between Income and Gas Prices', x='Income', y = 'Gas Prices') +
  theme_minimal()
```

### Description:
The claim for this part is that the richer the area, the higher the gas prices in Austin. To be able to prove this theory, we fit a linear model for price versus income and then did a bootstrap between those two variables. After doing the boot strap sample 10,000 times, the evidence shows that the regression model in price between gas stations and income is somewhere between 6.764848e-07 and 1.778617e-06, with 95% confidence. The jitter plot is the visual summary of this theory. The plot shows the relationship between Income (x axis) and the Gas Prices (y axis). It is concluded that the theory is supported because the 95% confidence interval does not contain 0, so the slope estimate is thus “statistically significant” at the 5% level.

## Part C
```{r echo=FALSE, message=FALSE}
gas_stoplight = do(10000)*diffmean(Price ~ Stoplight,
data=resample(gas))
ggplot(gas_stoplight) + 
  geom_histogram(aes(x= diffmean), col = 'black', fill = 'lightsalmon') + labs(title = 'Distribution of the Difference Mean of Stoplights and Gas Prices', x='Diffmean of Stoplight and Price') + theme_minimal()
confint(gas_stoplight, level = 0.95)
```
### Description:
The claim for this section is that Austin gas stations charge more if there are stoplights. To be able to prove this theory, there was a bootstrap sample done with the gas station price and the stoplights in Austin. After doing the boot strap sample 10,000 times, the evidence shows that the difference in price between gas stations and stoplights is somewhere between -0.03778 and about 0.0308, with 95% confidence. The histogram is the visual  summary of this theory and shows the distribution of the difference mean between stoplights and price (x axis). The graph is approximately symmetrical. The median is approximately `r round(median(gas_stoplight$diffmean),2)`. The 25th percentile is about `r round(quantile(gas_stoplight$diffmean, .25),2)` and the 75th percentile is about `r round(quantile(gas_stoplight$diffmean, .75),2)`.It is concluded that the theory is unsupported because the 95% confidence interval does contain 0, so the mean difference is thus “statistically insignificant” at the 5% level.

# Part D:
```{r echo=FALSE, message=FALSE}
gas_highway = do(10000)*diffmean(Price ~ Highway,
data=resample(gas))
ggplot(gas_highway) + 
  geom_histogram(aes(x= diffmean), col = 'black', fill = 'lightskyblue2') + labs(title = 'Distribution of the Difference Mean of Highway and Gas Prices', x='Diffmean of Highway and Price') + theme_minimal()
confint(gas_highway, level = 0.95)
```

### Description:
The claim for this part is that the gas stations in Austin with direct highways charge more. To be able to prove this theory, there was a bootstrap sample done with the gas station price and the highways in Austin. After doing the boot strap sample 10,000 times, the evidence shows that the difference in price between gas stations and highways is somewhere between 0.00979 and 0.08106, with 95% confidence. The histogram is the visual summary of this theory and shows the distribution of the difference mean between highways and price (x axis). The graph is approximately symmetrical. The median is approximately `r round(median(gas_highway$diffmean),2)`. The 25th percentile is about `r round(quantile(gas_highway$diffmean, .25),2)` and the 75th percentile is about `r round(quantile(gas_highway$diffmean, .75),2)`.It is concluded that the theory is supported because the 95% confidence interval does not contain 0, so the mean difference is thus “statistically significant” at the 5% level.

# Part E
```{r echo=FALSE, message=FALSE}
gas_brand = gas %>%
  mutate(Shell = ifelse(Brand == 'Shell', 'Y', 'N'))
gas_shell = do(10000)*diffmean(Price ~ Shell,
data=resample(gas_brand))
ggplot(gas_shell) + 
  geom_histogram(aes(x= diffmean), col = 'black', fill = 'midnightblue') + labs(title = 'Distribution of the Difference Mean of Brands and Gas Prices', x='Diffmean of Brands and Price') + theme_minimal()
confint(gas_shell, level = 0.95)
```

### Description:
The claim for this part is that the gas stations in Austin with the brand Shell charges more than all other non-Shell brands. To be able to prove this theory, a new variable of brands, either being the Shell brand or not, had to be made using the mutate function and then there was a bootstrap sample done with the gas station price and the brands in Austin using the new data set made. After doing the boot strap sample 10,000 times, the evidence shows that the difference in price between gas stations and highways is somewhere between -.01015 and 0.0656, with 95% confidence. The histogram is the visual summary of this theory and shows the distribution of the difference mean between brands and prices (x axis). The graph is approximately symmetrical. The median is approximately `r round(median(gas_shell$diffmean),2)`. The 25th percentile is about `r round(quantile(gas_shell$diffmean, .25),2)` and the 75th percentile is about `r round(quantile(gas_shell$diffmean, .75),2)`.It is concluded that the theory is not supported because the 95% confidence interval does contain 0, so the mean difference is thus “statistically insignificant” at the 5% level.

# Problem 2

## Part A
```{r echo=FALSE, message=FALSE}
mercedes_2011 <- mercedes %>%
  filter(year == 2011, trim == "63 AMG")
mileage_2011 = do(10000)*mean(~mileage, data=resample(mercedes_2011))
confint(mileage_2011, level = 0.95)
```

### Description:
We are 95% confident that the true average mileage of 2011 S-Class 63 AMGs lies between [26267, 31729] based on the bootstrap re sampling. Since the 95 % confidence interval does not contain 0, the average mileage is concluded that it is "statistically significant" at the 5% level. 

## Part B
```{r echo=FALSE, message=FALSE}
mercedes_2014 <- mercedes %>%
  filter(year == 2014, trim == "550") %>%
  mutate(isBlack = ifelse(color == 'Black', 'TRUE', 'FALSE'))
mercedes_bootstrap = do(10000)*prop(~isBlack, data=resample(mercedes_2014))
confint(mercedes_bootstrap, level = 0.95)
```

### Description:
We are 95% confident that the proportion of all 2014 S-Class 550s that were painted black for a sample of 2889 lies between [0.417,0.454] based on the bootstrap re sampling. Since the 95 % confidence interval does not contain 0, the proportion of painted black cars is concluded to be "statistically significant" at the 5% level. 

# Problem 3

## Part A
```{r echo=FALSE, message=FALSE}
show_filter <- nbc_shows %>%
  filter(Show == "Living with Ed"| Show == "My Name is Earl") 
happy_show = do(10000)*diffmean(Q1_Happy ~ Show,
data=resample(show_filter))
confint(happy_show, level = 0.95)
```

### Description:
Who makes people happier: the show “Living with Ed” or “My Name is Earl.”?; to be able to answer this question, I first filtered the two shows by using the filter and piping function to do the bootstrap re sample 10,000 times of the difference mean between the two shows on the Q1_Happy question. After bootstrapping, I used the confint function to calculate the evidence that shows that the difference in ratings for the happy question between “Living with Ed” and “My Name is Earl.” is somewhere between -.3987585 and 0.1056519, with 95% confidence. Based off of the evidence, there is no show that produces a consistent higher mean value because the 95% confidence interval contains a 0, making the difference  statistically insignificant at the 5% level.

## Part B
```{r echo=FALSE, message=FALSE}
partb_filter <- nbc_shows %>%
  filter(Show == "The Biggest Loser" | Show == "The Apprentice: Los Angeles") 
annoyed_show = do(10000)*diffmean(Q1_Annoyed ~ Show,
data=resample(partb_filter))
confint(annoyed_show, level = 0.95)
```

### Description: 
Which reality/contest show made people feel more annoyed: “The Biggest Loser” or “The Apprentice: Los Angeles.”?; to be able to answer this question, I first filtered the two shows by using the filter and piping function to do the bootstrap re sample 10,000 times of the difference mean between the two shows on the Q1_Annoyed question. After bootstrapping, I used the confint function to calculate the evidence that shows that the difference in ratings for the annoyed question between "The Biggest Loser” and “The Apprentice: Los Angeles.” is somewhere between -.5129492 and -0.02272205, with 95% confidence. Based off of the evidence, there is a show that produces a consistent higher mean value because the 95% confidence interval does not contain a 0, making the difference statistically significant at the 5% level; the estimate is about -.270997, so most feel annoyed to watch "The Apprentice: Los Angeles" compared to "The Biggest Loser."

## Part C 
```{r echo=FALSE, message=FALSE}
dance_show <- nbc_shows %>%
  filter(Show == "Dancing with the Stars") %>%
  mutate(Confusing_Rating = ifelse(Q2_Confusing %in% c(4, 5), 'Agreed', 'Disagreed'))
confused_bootstrap = do(1000)*prop(~Confusing_Rating, data=resample(dance_show))
confint(confused_bootstrap, level = 0.95)
```

### Description:
What proportion of American TV watchers would we expect to give a response of 4 or greater to the “Q2_Confusing” question for "Dancing with the Stars"?; to be able to answer this question, I first filtered the show by using the filter and the mutate function to make a variable of Agreed (4 or 5 Rating) and Disagreed (lower than 4 rating) to the Q2_Confused question. Then I did the bootstrap re sample 10,000 times of the proportion of the response of 4 or greater to the “Q2_Confusing” question and used the confint function to calculate the evidence that shows that the proportion in ratings for the confused question for "Dancing with the Stars" is somewhere between 0.04406077 and 0.1160221, with 95% confidence. Based off of the evidence, the 95% confidence interval is statistically significant because there is no 0 in the interval, so the proportion is somewhere between the confidence interval with an estimate of about 0.07734807. 

# Problem 4 
```{r echo=FALSE, message=FALSE}
ebay_experiment = do(10000)*diffmean(rev_ratio ~ adwords_pause,
data=resample(ebay))
confint(ebay_experiment, level = 0.95)
```

### Description:
Does eBay's paid advertising on Google's search platform lead to a significant difference in revenue ratios between the treatment group (where advertising on Google AdWords was paused for a month) and the control group (where advertising on Google AdWords continued as before)? The statistical approach I did to solve this question was doing the boot strap sample 10,000 times for the difference mean between the control and treatment group over the revenue ratio; the evidence shows that the difference in revenue ratio between the treatment and control group is somewhere between -0.09142365 and -0.01288091, with 95% confidence. Since the 95% confidence interval does not contain 0, it is concluded that the mean difference is thus “statistically significant” at the 5% level, and it can be assumed that the ads create revenue for eBay. 